Bathtub Qualitative Reasoning

### 2016-10-20 paper.tex
plt
update

\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{pdfpages}
\usepackage{float, algorithmic, algorithm2e, program}
\usepackage{tabularx}
\usepackage{longtable}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}[section]

@@

\section{Problem}

@@

\begin{figure}[H]
\includegraphics[]{problem.png}
\caption{Drawings of the causal model active for the system}
\end{figure}

\begin{algorithm}
\If{condition}{then-block}
\caption{Drawings of the causal model active for the system}
\end{algorithm}

>>>>

\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{pdfpages}
\usepackage{float, algorithmic, algorithm2e, program}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{epstopdf}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}[section]

@@

\section{Base Problem}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.5]{problem1.eps}
\caption{Drawings of the causal model active for the problem}
\end{figure}

\section{Algorithm}

\begin{algorithm}
\If{condition}{then-block}
\caption{}
\end{algorithm}

\section{State-graph}

\section{Extra Problem}

\begin{itemize}
\item \textbf{Quantities:}
\begin{itemize}
\item Inflow (of water into the container) $\in [0, +]$
\item Outflow (of water out of the container) $\in [0, +, Max]$
\item Volume (of the water in the container) $\in [0, +, Max]$
\item Height (of the water column in the container) $\in [0, +, Max]$
\item Pressure (of the water column at the bottom of the container) $\in [0, +, Max]$
\end{itemize}

\begin{itemize}
\item I+(Inflow, Volume): the amount of inflow increases the volume
\item I-(Outflow, Volume): the amount of outflow decreases the volume
\item P+(Volume, Height): height changes are proportional to volume changes
\item P+(Height, Pressure): pressure changes are proportional to height changes
\item P+(Pressure, Outflow): outflow changes are proportional to pressure changes
\item V(Volume(Max), Height(Max)): the height is at its highest value (Max), when the volume is at it highest value
\item V(Volume(0), Height(0)): there is no height, when there is no volume
\item V(Height(Max), Pressure(Max)): the pressure is at its highest value (Max), when the height is at it highest value
\item V(Height(0), Pressure(0)): there is no pressure, when there is no height
\item V(Pressure(Max), Outflow(Max)): the outflow is at its highest value (Max), when the pressure is at it highest value
\item V(Pressure(0), Outflow(0)): there is no outflow, when there is no pressure
\end{itemize}
\end{itemize}

\begin{figure}[H]
\centering
\includegraphics[scale=0.5]{problem_extra.eps}
\caption{Drawings of the causal model active for the extra problem}
\end{figure}
